*flippant* -- An R package for the automated analysis of dithionite scramblase

### 2015-10-18 inst/manuscript/manuscript.rmd
Add a reference to the git hash at the time of compilation;
Enable compilation to all formats;

---
title: '*flippant* -- An R package for the automated analysis of dithionite scramblase
  assays'
author: Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^,
  Michael A. Goren ^‡^ and Anant K. Menon ^‡^
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
#  word_document
  pdf_document:
    fig_caption: yes
csl: bioinformatics.csl
bibliography: flippant.bib
---

@@

>>>>

---
title: '*flippant* -- An R package for the automated analysis of dithionite scramblase
  assays'
author: Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^,
  Michael A. Goren ^‡^ and Anant K. Menon ^‡^
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
  pdf_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
  html_document:
    fig_caption: yes
csl: bioinformatics.csl
bibliography: flippant.bib
---

@@

Current Git Hash
:   `r system("git log -1 --format='%H'", intern = TRUE)`
